Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-26 docs/paper.tex
Made spelling consistent with en_US

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs. The second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.

@@

		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work. 

@@

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the color of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. This comparison data originates in \cite{donszelmann2021}. The values compared are the fraction of instances solved, and the average runtime per instance. It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

@@

	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0Ghz with 8GiB of RAM. All 200 maps were used for each setting.

>>>>

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs. The second agent staying at node D after completing the path is also modeled in its MDD to ensure that the place remains blocked.

@@

		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixed point is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work. 

@@

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the color of the center goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. This comparison data originates in \cite{donszelmann2021}. The values compared are the fraction of instances solved, and the average run time per instance. It should be noticed that in the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

@@

	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM. All 200 maps were used for each setting.
